---
title: "phytoData"
author: "B"
date: "Tuesday, October 27, 2015"
output: html_document
---
```{r setup, include=FALSE, echo=FALSE, cache=FALSE} 
#########function to install (if needed) and load R packages by list
libs<-c("RODBC","dplyr") #list of packages to load

installLoad<-function(pck){ #user defined function
    if(!pck%in%installed.packages()){install.packages(pck)}
    require(pck, character.only = TRUE)
  }
lapply(libs,function(x) installLoad(x))  #Load/Install require packages
```

To Do List
-------------------------
* everything


Introduction
-------------------------
Work with the NLA 2007 phytoplankton data

Data Steps
-------------------------

* get the phyto softcount data from waterbodydatabase.mdb

###Data Definitions

Field  | Units | Description
------------- | ------------- | -------------
**SITE_ID** | (char) |Unique site identification number
**VISIT_NO** | (num) |Lake visit number. 1-1st field sampling visit; 2-2nd field sampling visit
**DATE_COL** | (date) |Date of site visit
**SAMPLED_PHYT** | (char) |Phytoplankton sample collected?
**SAMPLE_CATEGORY** | (char) |(P)rimary or Field (D)uplicate
**INDXSAMP_PHYT** | (YES/NO) |Index phytoplankton sample for site (YES/NO)-typically the Visit 1 Primary sample
**SAMPLE_TYPE** | (char) |Type of sample (soft ALGAE/DIATOM)
**SAMPLE_DEPTH** | (m) |Depth of integrated sample (typically 2 m)
**TAXATYPE** | (cells/ml) |Type of algae
**OTU** | (char) |Operational Taxonomic Unit 
**ABUND** | (char) |Abundance (char)
**DIVISION** | (char) |Division name (from taxa list)
**ORDER** | (char) |Order name (from taxa list)
**FAMILY** | (char) |Family name (from taxa list)
**GENUS** | (char) |Genus name (from taxa list)
**SPECIES** | (char) |Species name (from taxa list)
**VARIETY** | (char) |Variety name (from taxa list)

```{r phytoData, include=FALSE, echo=FALSE, cache=FALSE} 
# Read data-****Make Sure the Path Is Correct****
con <- odbcConnectAccess("c:/bryan/EPA/Data/WaterbodyDatabase/WaterbodyDatabase.mdb")
phyto<- sqlQuery(con, "
SELECT tblNLA_nla_phyt_softcount_20091023.SITE_ID, tblNLA_nla_phyt_softcount_20091023.VISIT_NO, tblNLA_nla_phyt_softcount_20091023.DATE_COL, tblNLA_nla_phyt_softcount_20091023.SAMPLED_PHYT, tblNLA_nla_phyt_softcount_20091023.SAMPLE_CATEGORY, tblNLA_nla_phyt_softcount_20091023.INDXSAMP_PHYT, tblNLA_nla_phyt_softcount_20091023.SAMPLE_TYPE, tblNLA_nla_phyt_softcount_20091023.SAMPLE_DEPTH, tblNLA_nla_phyt_softcount_20091023.TAXATYPE, tblNLA_nla_phyt_softcount_20091023.OTU, tblNLA_nla_phyt_softcount_20091023.ABUND, tblNLA_nla_phyt_softcount_20091023.DIVISION, tblNLA_nla_phyt_softcount_20091023.FAMILY, tblNLA_nla_phyt_softcount_20091023.ORDER, tblNLA_nla_phyt_softcount_20091023.GENUS, tblNLA_nla_phyt_softcount_20091023.SPECIES, tblNLA_nla_phyt_softcount_20091023.VARIETY
FROM tblNLA_nla_phyt_softcount_20091023;
")
close(con)
#str(phyto)
```